(TBD): Feedback and Chemical Evolution in Low Mass Dwarf Galaxies III: Role of Feedback in Regulating Metal Enrichment of Stars and the ISM

### 2017-12-14 main.tex
Project created

\documentclass[twocolumn]{aastex61}
\pdfoutput=1 %for arXiv submission
\usepackage{amsmath,amstext}
\usepackage[T1]{fontenc}
\usepackage{apjfonts} 
\usepackage[figure,figure*]{hypcap}
\usepackage{multirow}
\usepackage{mathtools}
\renewcommand*{\sectionautorefname}{Section} %for \autoref
\renewcommand*{\subsectionautorefname}{Section} %for \autoref

\shorttitle{Feedback with Individual Stars}
\shortauthors{Emerick, Bryan, Mac Low}
\newcommand{\msun}{M$_{\odot}$}
\newcommand{\ccunit}{cm$^{-3}$}

@@

\title{REDO Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution I: Methods and Test Case}
%Unstable Star Formation for the Lowest Mass Dwarf Galaxies
\author{Andrew Emerick}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
\author{Greg Bryan}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
\author{Mordecai-Mark Mac Low}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}

%\affiliation{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, Heidelberg, Germany}

\begin{abstract}
\textbf{Saving this for after the first iteration}
\end{abstract}

\keywords{Galaxy -- Hydrodynamics -- Simulation -- Feedback}

@@

Cosmological simulations of galaxy evolution have shown increasing agreement with observations over the past decade. Recent works have been able to well capture the star forming main sequence, the stellar mass to halo mass relationship, mass metallicity relationship, etc. \citep[e.g.][]{EAGLE,Illustris1,Illustris2,FIRE,Dave2017} across a wide range of galaxy masses. On small scales, simulations have been able to resolve the long standing disagreement between $\Lambda$CDM cosmology and observed galaxies on the low-mass end without invoking new physics beyond $\Lambda$CDM. This includes the missing satellites problem \citep{Moore1999,Klypin1999}, too big to fail \citep{MBK2011,MBK2012,GK2014}, and the observed coring of inner dark matter profiles \citep[e.g.][]{Oh2011}. See both \citet{SomervilleDave2015} and \citet{NaabOstriker2016} for recent reviews on these topics.

These simulations generally owe their successes to a combination of better accounting of the baryonic physics that governs galaxy evolution and higher resolution. In particular, a detailed accounting of both multi-channel stellar feedback processes and AGN has shown significant promise over schemes that include supernovae alone, albeit at much greater computational expense. In spite of this progress, practical considerations still limit large cosmological simulations to using sub-grid, phenomenological feedback models, often tuned to reproduce observed galaxy relationships. For this reason, we still have yet to arrive at a complete, self-consistent picture of how feedback governs galaxy evolution.

Due to its complexity, the detailed interstellar medium (ISM) and chemical abundance properties, beyond total metallicity, are sensitive tests of the underlying physical processes that govern galaxy evolution. Examining these in more detail in galaxy scale simulations is an important and exciting new discriminator between models. There is a considerable body of work examining the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}. These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017} and more detailed quantities such as metallicity distribution functions (MDFs) and abundance evolution of individual species \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} . However, there is a general lack of numerical diversity in these works, as a majority are implemented in some flavor of smoothed particle hydrodynamics (SPH) schemes. Given the known differences between hydrodynamics implementations \citep{Agertz2007,AGORA,AGORA2}, extending these models to a grid-based code is a valuable and complementary approach towards investigating galactic chemical evolution that has only been done recently \citep{Few2012,Few2014,Vorobyov2015}. Additionally, grid-based schemes are able to generally avoid issues with metal mixing, one of the largest model uncertainties in standard SPH codes.

The native SPH scheme is incapable of capturing mixing between chemically inhomogeneous particles, as necessary for chemical evolution. This must be handled through sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010, Shen2013,Brook2014,Su2017} which, while sophisticated, must still generally be fine-tuned. Even more, a given parameterization is not necessarily applicable generally \citep{Revaz2016}, though recent studies have shown great improvements to this end \citep{Escala2017}. Metal mixing efficiencies may also vary species-by-species (refs), as suggested by recent work \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017}. In part, this is because mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) 
%mm in which they are injected to
    that injects metals into 
the ISM. The variations in how one handles sub-grid metal injection and metal mixing schemes can lead to challenges in connecting models back to the fundamental physics that drives galactic evolution. We seek to produce a complementary approach to studying galactic chemical evolution with a new chemical evolution scheme implemented in the adaptive mesh refinement code \texttt{Enzo} designed for high resolution simulations of isolated galaxies.

Although increasing physical resolution reduces 
%mm one's 
reliance on sub-grid physics, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations \citep[SSPs; as studied in detail in ][]{Revaz2016} do not make physical sense. Below 10$^4$ M$_{\odot}$, SSPs begin to no longer fully sample the IMF, and can no longer be considered average representations of stellar populations; this becomes conceptually problematic at SSP masses comparable to or below the mass of the most massive star ($\sim 100$ M$_{\odot}$). Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Rosdahl2015,Kroupa2013}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}. 
%mm Perhaps the most naive, 
   The most straightforward
solution, though untenable for large scale simulations, is to remove the SSP formalism entirely and simply track stars as individual particles. In this work, we 
%mm follow stars as individual star particles, allowing us to place unprecedented detail on our
     do this, allowing unprecedented detail in our
 accounting of stellar feedback processes and chemical enrichment.

The relative simplicity of idealized, isolated galaxy evolution simulations allows for a focused, first-principles approach to studying multi-channel feedback mechanisms. We follow recent work using low mass dwarf galaxies as laboratories to study in detail how feedback governs galaxy evolution. For example, \citet{Forbes2016} found that photoelectric heating can be a significant source of feedback in small galaxies. \citet{Hu2016} and \citet{Hu2017} examined the relative importance of various feedback physics in regulating ISM properties of dwarf galaxies. Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advancements: 1) direct star-by-star modeling, 2) stellar wind feedback, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation.

Using star-by-star modeling, we are able to capture in more detail the stellar yields from individual stars released over their lifetime. In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars. This opens an exciting new channel for testing models of galaxy evolution by enabling us to leverage current and ongoing observations probing the detailed chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}.

This paper is the first in a series of papers examining in detail the role that the individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution. In this paper we introduce a new method of modeling for feedback physics and galactic chemical enrichment in the cosmological, hydrodynamics code \texttt{Enzo}. For the first time in galaxy-scale simulations, we model star formation down to particles representing individual stars, while simultaneously capturing stellar feedback through stellar winds, core collapse and Type Ia supernovae, photoelectric heating, and ionizing radiation through ray-tracing radiative transfer. In addition, we couple to a self-consistent set of stellar yields 
%mm tables from the
to track stellar yields from massive star stellar winds, AGB star winds, and supernovae. We describe each mode of our multi-channel feedback 
%mm implementation 
in detail below, and briefly discuss their implementation in an isolated dwarf galaxy simulation.

Readers who may want to only briefly skim (or skip) over the details of our included physics are advised to just read the beginning of Section~\ref{sec:methods}, which contains a complete---yet brief---summary of the included physics.

\section{Methods}
\label{sec:methods}
In 
%mm brief, 
     summary, 
we produce high-resolution galaxy-scale simulations tracking stars not as SSP's, but as individual stars sampled from an assumed IMF.
This allows us to follow star-by-star variations in feedback physics and stellar yields in detail. To properly model the ISM, we track non-equilibrium primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic UV background. We 
%mm 
    assume collisional ionization equilibrium for all other elements in order to
use updated \texttt{Cloudy} metal line cooling tables consistent with our self-shielding approximation (see Appendix ~\ref{appendix:cooling}), and an updated observationally motivated dust model for the low metallicity regimes studied here (Z $\lesssim 0.1$ Z$_{\odot}$). Each star is assigned basic properties (surface gravity, effective temperature, radius, lifetime) from tabulated stellar evolution models, which inform how the stars deposit their feedback. We directly track ionizing radiation from massive stars using an adaptive ray tracing radiative transfer method that includes the effects of radiation pressure. In addition, we follow the optically thin non-ionizing UV radiation from these stars leading to photoelectric heating and Lyman-Werner (LW) dissociation of molecular hydrogen. We track the stellar wind feedback and supernovae from these stars, depositing individual metal yields from both. We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia supernovae progenitors. We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star
%mm
   as it forms
with the associated local gas abundances for each species. These methods are discussed in full detail below.

\subsection{Hydrodynamics and Gravity}
\label{sec:hydro}

We use the adaptive mesh refinement (AMR) hydrodynamics and N-body code \texttt{Enzo}\footnote{http://www.enzo-project.org} to simulate the chemodyanamical evolution and detailed feedback physics in a set of high resolution, isolated, low mass dwarf galaxies. \texttt{Enzo} is an open-source code that is undergoing continual, active development by many researchers across several institutions. We use a substantially modified version of the current development version of \texttt{Enzo} (version 2.X) in this work.\footnote{This version is contained in a publicly available fork of the main repository: https://bitbucket.org/aemerick/enzo-emerick. Specifically, simulations presented here were conducted at changeset 445de816fd99.} We solve the equations of hydrodynamics using a direct-Eulerian piecewise parabolic method \citep{ColellaWoodward1984, Bryan1995} and a two-shock approximate Riemann solver with progressive fallback to more diffusive Riemann solvers in the event that higher order methods produce negative densities or energies. We compute the total gravitational potential from gas self-gravity, stars, and static background dark matter potential. The collisionless star particles are evolved with a particle-mesh N-body solver at an effective force resolution of $\sim 2 \Delta x$, where $\Delta x$ is the local cell size.

The computational domain in an AMR simulation is adaptively refined up to a designated resolution limit for a given set of refinement criteria. We require that the Jeans length be resolved by a minimum of 8 cells, continually refining a given region until this criteria is met or the region reaches the maximum resolution. Our maximum resolution in the simulations presented here is 1.8 pc. At maximum resolution, the Jeans length can become under resolved, leading to artificial numerical fragmentation. Studies have shown that resolving the Jeans length by at least 4 cells is required to suppress this fragmentation \citep{Truelove1997}.

We set the star formation density threshold to the value at which the Jeans length becomes resolved by only 4 cells in sub-200 K gas, or about 200 \ccunit (as discussed further in Section~\ref{sec:star formation}). Forming stars from this gas will reduce the local density, ensuring the Jeans length is resolved. However, since star formation is not instantaneous, we employ a pressure floor to support gas against artificial collapse once its Jeans length becomes unresolved. This prevents dense, self-gravitating gas from rapidly reaching densities significantly above our resolution limit. The use of a pressure floor is common in galaxy scale simulations with limited dynamic range. (\textbf{I contrasted this to Hu's work which allows arbitrarily high densities, hoping feedback mitigates how high the densities actually get, but took it out. Leave it in?})

\subsection{Chemistry and Cooling Physics}
\label{sec:chemistry}

We use the chemistry and cooling library \texttt{Grackle}\footnote{https://grackle.readthedocs.io/en/grackle-3.0/} v 3.0 to follow a nine species non-equilibrium chemistry network (H, H$^+$, He, He$^+$, He$^{++}$, e$^{-}$, H$_2$, H$^{-}$, and H$_{2}$) which includes radiative heating and cooling from these species and metals.\footnote{We use a slightly modified version of the the main \texttt{Grackle} repository, available at https://bitbucket.org/aemerick/grackle-emerick at changeset 59adc76b3130.} \texttt{Grackle} is a freely available, open source multi-code library, designed to interface with a wide variety of astrophysical codes. We outline specific model choices made in our simulations and refer the reader to \citet{GrackleMethod} for a detailed discussion of the code. We apply the \citet{Glover2008} three-body rate for H$_{2}$ formation and include a model for H$_2$ formation on dust, dust heating, and dust cooling following the methods in \citet{2000ApJ...534..809O} and \citet{2005ApJ...626..627O} as included in \texttt{Grackle}. However, we update the default dust to gas ratio scaling in \texttt{Grackle} to account for the steeper scaling in low metallicity regimes ($Z \lesssim 0.1 Z_{\odot}$) with the broken power law scalings from \citet{Remy-Ruyer2014}. For metallicities above $\sim 0.1 Z_{\odot}$, this is equivalent to the the default behavior of \texttt{Grackle}, where dust content scales linearly with metallicity.
% Since we assume a dust abundance that depends only on metallicity, we do not track dust destruction or creation, which may play an important role regulating detailed ISM properties. (Vogelsberger is working on this directly but no papers yet... will cite if it gets submitted by then)

Metal line cooling is modeled using pre-computed \texttt{Cloudy}\footnote{http://www.nublado.org/} tables interpolated as a function of density, temperature, and redshift, using the \citet{HM2012} UV metagalactic background. As discussed in more detail in Section~\ref{sec:diffusive heating}, we account for approximate self-shielding of H and He against this UV background. Using this prescription with metal line cooling tables computed under an optically thin assumption can lead to an order of magnitude overestimation of the cooling rate at certain densities. To address this issue, we use re-computed metal line tables consistent with the self-shielding approximation.  We have made these new tables public in the main \texttt{Grackle} repository. These are both discussed in greater detail in Appendix ~\ref{appendix:cooling}.

\subsection{Star Formation Algorithm}
\label{sec:star formation}
In order to resolve individual star formation on galaxy scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}. Each cell at the maximum refinement level is capable of forming stars if it meets the following local criteria: 1) $n_{\rm cell} > n_{\rm thresh}$, 2) $T_{\rm gas} < T_{\rm thresh}$, 3) $M_{\rm gas} > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local Jeans mass. Our fiducial values for $n_{\rm thresh}$ and $T_{\rm thresh}$ are 200~cm$^{-3}$ and 200~K respectively. We limit the fraction of a cell's gas mass that is converted into stars by requiring $M_{\rm gas} > f_{\rm thresh} M_{\rm max,*}$, where $f_{\rm thresh} = 2.0 $ and $M_{\rm max,*}$ is the maximum star mass (100 M$_{\odot}$). No star formation occurs when $M_{\rm gas} < f_{\rm thresh} M_{\rm max,*}$, ensuring that a star formation episode does not produce negative densities.

We make the common ansatz that star formation occurs by converting some fraction of gas into stars in a free fall time ($\tau_{\rm ff}$) as characterized by a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$. At high resolution, one's choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2017, FIRE2}, as star formation is ultimately self-regulated by feedback.
%but we find that $\epsilon_{\rm f}$ may impact star formation in the lowest mass halos, which are unusually sensitive to stellar ionization feedback (see Emerick et. al. in prep).
The gas mass converted to stars in a time step, $dt$, is
\begin{equation}
M_{ {\rm gas} \to *} = \epsilon_{\rm f} M_{\rm gas} \frac{dt}{\tau_{\rm ff}}.
\end{equation}
In practice, $dt/\tau_{\rm ff} \ll 1$, and $M_{ {\rm gas} \to *}$ is smaller than the minimum star particle mass at parsec scale resolution. We therefore allow star formation to proceed stochastically, following the methods in \citet{Goldbaum2015, Goldbaum2016}, modified for variable stellar masses. In each cell that could potentially form stars, we compute the probability that 100 M$_{\odot}$ of gas will be converted into stars in that time step, and use a random number draw to determine whether or not star formation actually occurs. If it does, we random sample over the adopted IMF until 100 M$_{\odot}$ of stars form, keeping the last sampled particle if the total stellar mass formed exceeds 100 M$_{\odot}$. We make the simple assumption of a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over a minimum stellar mass of 1 M$_{\odot}$ and maximum stellar mass of 100 M$_{\odot}$.

Formed stars are deposited with random positions within the star forming cell and assigned velocities equal to the cell bulk velocity with a 1~km~s$^{-1}$ velocity dispersion. Stars are assigned metallicities corresponding to the metallicity of the star forming zone, and are chemically tagged with the 17 individual species abundances (H, He, and the 15 metals) that we follow in our simulations. Stars evolve during the simulation, by losing mass from stellar winds and supernovae as described below, and by changing types, but persist throughout the entire simulation. For example, low mass stars are tagged as white dwarfs at the end of their life, which may eventually explode as a Type Ia supernova (discussed below), after which they persist as massless tracer particle ``remnants''.

Finally, each star is marked as a ``must refine" particle, requiring that each star be surrounded by a four-cell region at the highest level of refinement. This ensures that both stellar winds and supernovae feedback are maximally resolved, and that any ejected yields are deposited over a consistent physical scale throughout the simulation.

\subsection{Stellar Properties}
\label{sec:properties}
Given each star's birth mass and metallicity, we interpolate over the PARSEC grid of stellar evolution tracks \citep{Bressan2012} to assign a lifetime and AGB phase start time (if any) to it, as well as the effective temperature $T_{\rm eff}$ and surface gravity $g$ used in computing radiation properties (see Section \ref{sec:ionizing radiation}). We use the largest subset of the PARSEC models that are regularly sampled in our mass/metallicity space of interest, with 26 mass bins over M$_{*} \in \left[0.95, 120.0 \right] {\rm M_{\odot}}$ and 11 metallicity bins over $Z \in \left[10^{-4}, 0.017 \right]$. Although $T_{\rm eff}$ and $g$ evolve over time for stars, modifying stellar radiative properties, following a stellar evolution track for each of our stars is beyond the scope of this work. We instead fix these properties at their zero age main sequence values.

\subsection{Stellar Feedback and Chemical Yields}

\subsubsection{Stellar Yields}
\label{sec:yields}
For the first time in galaxy scale simulations, we track galactic chemodynamical evolution using stellar yields as ejected from star particles that represent individual stars. We adopt the NuGrid\footnote{http://www.nugridstars.org} collaboration's set of stellar yields given on a uniformly sampled grid in stellar mass and metallicity with 12 mass bins over $M_{*} \in \left[1.0, 25.0\right]$ M$_{\odot}$ and five metallicity bins at $Z =$ 0.02, 0.01, 0.006, 0.001, and 10$^{-4}$ \citep{Pignatari2016, Ritter2017}. This grid includes yields from the AGB phase of stars between 1 and 7 M$_{\odot}$, as well as yields from both stellar winds and core collapse supernova of massive stars over 12 to 25 M$_{\odot}$. We complement these tables with tables from Slemer et. al. (in prep), based on the PARSEC stellar evolution tracks \citep{Bressan2012, Tang2014} to track stellar winds for stars more massive than 25 M$_{\odot}$. We ignore supernova yields from these stars (see next paragraph). We combine all stable isotope yields for a given element into a single elemental abundance for all stable elements from hydrogen to bismuth. Although we can follow an arbitrary number of metal species, practical considerations 
%mm 
   of memory use 
prevent this in any given simulation. We refer the reader to previous uses of the NuGrid yields in one-zone galactic chemical enrichment models \citep{Cote2016,  Cote2016_feb,Cote2017} for a detailed discussion of how various model uncertainties can influence galactic chemical evolution.

Above some mass $M_{\rm trans}$ within the unsampled range of 7--12 M$_{\odot}$, stars do not undergo AGB wind phases and end their lives as core collapse supernovae. Where this transition occurs is uncertain, but is commonly taken to be around 8--10~M$_{\odot}$. This is a free parameter in our model, but we take $M_{\rm trans} = 8$~M$_{\odot}$ as our fiducial value. In our model, stars below this mass eject their wind yields in an AGB phase only at the end of their lives, typically over a period comparable to or less than a few time steps ($\lesssim 10$ kyr). Stars above this mass 
%mm
    are assumed to
eject their stellar yields via 
%mm ``massive" 
   line-driven
stellar winds at a constant mass loss rate throughout their lifetime
%mm ,
  (neglecting Wolf-Rayet and luminous blue variable phases),
ending their lives as a core-collapse supernova (see Section \ref{sec:stellar winds} for details on the wind energetics). Varying $M_{\rm thresh}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of a 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds. \citet{Cote2017} explores how the choice of $M_{\rm thresh}$ affects galaxy abundances in a one-zone model.

>>>>

\documentclass[twocolumn]{aastex61}
\pdfoutput=1 %for arXiv submission
\usepackage{amsmath,amstext}
\usepackage[T1]{fontenc}
\usepackage{apjfonts} 
\usepackage[figure,figure*]{hypcap}

\renewcommand*{\sectionautorefname}{Section} %for \autoref
\renewcommand*{\subsectionautorefname}{Section} %for \autoref

\shorttitle{Dwarf Galaxy Feedback}
\shortauthors{Emerick, Bryan, Mac-Low}

@@

\title{(TBD): Feedback and Chemical Evolution in Low Mass Dwarf Galaxies III: Role of Feedback in Regulating Metal Enrichment of Stars and the ISM}

%\title{Simulating Dwarf Galaxy Evolution with Individual Star Feedback II: Importance of Dark Matter Halo Depth to Prevent Self-Quenching in the Lowest Mass Dwarf Galaxies}

\author{Andrew Emerick}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
\author{Greg Bryan}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
\author{Mordecai-Mark Mac Low}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}

\begin{abstract}
Abstract.
\end{abstract}

\keywords{}

@@

\section{Methods}
\label{sec:methods}
We refer the reader to Paper I for a detailed description of our numerical methods and feedback models, briefly summarized below.

\subsection{Hydrodynamics}
We use the adaptive mesh refinement (AMR) astrophysical hydrodynamics and N-body code \textsc{Enzo}\footnote{http://www.enzo-project.org} \citep{Enzo2014} in this work. \texttt{Enzo} is an open-source code that is undergoing continual, active development by many researchers across several institutions. We use a substantially modified version of the current development version of \texttt{Enzo} (version 2.X) in this work.\footnote{This version is contained in a publicly available fork of the main repository: https://bitbucket.org/aemerick/enzo-emerick. Specifically, simulations presented here were conducted at changeset 445de816fd99.}. We solve the equations of hydrodynamics in our isolated galaxy simulations using a direct-Eulerian piecewise parabolic method (PPM) \citep{ColellaWoodward1984, Bryan1995} and a two-shock approximate Riemann solver with progressive fallback to more diffusive solvers. We include the contribution of gas self-gravity to the local potential, and evolve the collisionless star particles using a particle mesh N-body solver.

Each galaxy is centered in a 128$^{3}$ zone computational domain with width equal to approximately 2 $R_{\rm vir}$ (see Section~\ref{sec:IC} and Table~\ref{table:IC}). We use 8 or 9 additional levels of refinement to reach a maximum resolution of $\sim$ 2 pc in each galaxy. A zone is refined 1) if the mass in a given cell exceeds $M_{\rm res} = 52 $~M$_{\odot}$, 2) such that the local Jeans length is always refined by 8 cells. In addition, regions within 4 cells of a star particle are refined to the maximum refinement level to ensure feedback is always deposited at maximum resolution. Our star formation density threshold corresponds roughly to densities where the Jeans length becomes unresolved at the maximum refinement level (discussed below). However, we use a pressure floor to prevent artificial fragmentation of this star forming gas.

\subsection{Star Formation and Stellar Feedback}
We refer the reader to Paper I for the complete details of our star formation and feedback methods, summarized below.

We allow star formation using a stochastic method \citep{Goldbaum2015,Goldbaum2016} that samples directly from an adopted IMF. In contrast to most other galaxy scale simulations to date, these star particles represent individual stars rather than populations of many stars. In each star forming region, defined as zones with $n > 200$~cm$^{-3}$, $T < 200$~K, and a convergent flow, we compute the probability that 100 M$_{\odot}$ of stars form in that region in that time step assuming the star formation rate depends on the local gas free-fall time and a star formation efficiency, which we take as $\epsilon_{\rm f} = 0.02$ (cite). Stars are sampled from a Salpeter IMF with $M_{*} \in [1,100]$~M$_{\odot}$.

We follow yields from 12 individual metal species using yields tables from XXXX for all stars with $M_{*} < 25$~M$_{\odot}$, and XXX for the stellar winds from stars with $M_{*} > 25$M$_{\odot}$. We make the simplifying assumption that all stars with $M_{*} > 25$M~$_{\odot}$ do not explode as supernovae, given the significant uncertainties in the end-of-life behaviors for stars in this regime (citations). We include three distinct feedback channels for each of our stars: 1) supernovae, both core collapse and Type Ia, 2) stellar winds, both from massive and AGB stars, and 3) stellar radiation from massive stars. Here, we define massive stars as those with birth masses greater than 8 M$_{\odot}$. 
% Stellar attributes, used to set their lifetimes and feedback properties, are interpolated from the ZAMS values on the PARSEC stellar evolution tracks given the initial mass and metallicity of each star.

Supernovae are injected as thermal feedback alone with $E_{\rm SN} = 10^{51}$~erg in a 3-cell radius region around the given star particle. We have demonstrated in Paper I (see Appendix) that we have sufficient resolution to resolve these explosions with thermal energy injection alone. Low mass stars are tracked as white dwarfs at the end of their lives, using a delay-time-distribution model to determine when, if at all, a  given white dwarf will explode as a Type Ia supernovae. We assume the energy injection from stellar winds is negligible, given the computational expense of following fast (10$^{3}$ km s$^{-1}$), hot ($\sim 10^{6}$~K) gas while satisfying the Courant condition. Rather, winds are injected as thermal energy, with wind temperature equal to the stellar surface temperature, and at $v_{\rm wind} = 1$ km s$^{-1}$. Confirming the common assumption that wind energy is not a significant long-term source of feedback in the evolution of these galaxies is the subject of ongoing work.

We follow stellar radiation in four bands. Two, HI and HeI ionizing radiation, are followed through direct ray-tracing methods from (cite). The other two, FUV and LW radiation, are assumed to be everywhere optically thin in these small, low metallicity dwarf galaxies. The stellar FUV radiation contributes to the local photoelectric heating rate using a prescription described in Paper I, similar to previous works \cite{BakesTielens1994,Wolfire2003,Forbes2016,Hu2017}. The LW radiation contributes to the local H$_{2}$ dissociation rates. These radiation fields are included in addition to the metagalactic UV background, discussed below.

% We follow the ionizing radiation from massive stars, $M_{*} > 8$~M$_{\odot}$, through direct radiative transfer (cite) using fluxes obtained from interpolation on the OSTAR2002 grid of stellar atmospheric properties. We also follow FUV and LW band radiation from these stars under the assumption that this non-ionizing radiation is optically thin. The FUV radiation is used to compute the local photoelectric heating rate using a model adopted from (bakes, wolfire, forbes).

% We follow stellar winds from both massive stars, assumed to be constant throughout their lifetime, and the AGB phases of less massive stars. Due to the computational expense of following these fast ($\sim 10^{3}$~km~s$^{-1}$) and hot ($T \sim 10^{6}$~K) winds, we inject these winds with low velocities and with thermal energy equivalent to the stellar effective temperature. We therefore assume that energy injection to the ISM from these winds to be negligible compared to the stellar radiation and supernova feedback (cite). Confirming the effects of a detailed stellar wind implementation on long-term galaxy evolution is the subject of future work.

%We track both core collapse supernovae from massive stars and Type Ia supernovae from low mass stars. The Type Ia supernovae are included self-consistently, using a delay time distribution model to compute the probability that a white dwarf formed from the low mass stars will explode in the simulation time, deterministically setting their explosion times.

\subsection{Heating and Cooling Physics}
\label{sec:heating and cooling}
We use the chemistry and cooling package Grackle \citep{GrackleMethod} to follow 9 species non-equillibrium primordial chemistry and approximate metal line cooling in our simulations. Our primordial cooling and heating rates are computed self-consistently with the non-equillibrium chemistry under a metagalactic UV background \citep{HM2012}. We account for approximate self-shielding against the UV background following \citep{Rahmati2013} and include use metal line cooling rates tabulated from \textsc{Cloudy}, accounting self-consistently for the reduced ionizing background in self-shielded regimes (see Paper I for more details on these tables). We also include both the LW radiation and photoelectric heating from the UV background.

\subsection{Initial Conditions}
\label{sec:IC}
Each galaxy in this work was initialized as a uniform distribution of gas set to be in hydrostatic equilibrium with a background, static dark matter potential. The gas properties in each galaxy remain fixed, modeled after the Local Group dwarf galaxy Leo P, as does the dynamical mass interior to 500 pc, set to $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$. In each of our four galaxies, we vary only the maximum circular velocity of the dark matter halo, and by extension $M_{\rm vir}$ and $R_{\rm vir}$, as described below.

The gas properties in each galaxy are designed to be similar to that of the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, but are not meant to be a matched model to this galaxy. Leo P is gas rich ($M_{\rm gas} > M_{*}$) and low metallicity, with $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to a radius $r_{\rm HI} = 500$~pc, and with $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or $Z \sim 5.4\times10^{-4}$ adopting $Z_{\odot} = 0.018$ from \cite{Asplund2009}. We initialize our dwarf galaxy without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$ (or $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$) and $Z = 4.3\times 10^{-4}$, comparable to the average $z = 0$ metallicity from the stellar models computed in \citep{McQuinn2015}. The gas density profile is set using an exponential disk (see Paper I) with scale radius and scale height of $250$~pc and $100$~pc respectively, with a total radial extent of 600~pc. The temperature and circular velocity profiles are set assuming hydrostatic equillibrium with the dark matter background, described below.

As mentioned, we fix the dynamical mass interior to 500 pc in each galaxy to the measured value in Leo P. This is equivalent to fixing the circular velocity at 500 pc, or $v_{\rm c, 500 \rm{pc}} = 15$~km~s$^{-1}$ as is observed for Leo P \citep{Bernstein-Cooper2014}. We represent our dark matter halo using a static Burkert potential \citep{Burkert1995}, and vary the maximum circular velocity by changing the adopted scale radius, $r_{\rm s}$. We do this for four different values of $v_{\rm c, max}$. Table~\ref{table: IC} gives the dark matter halo properties for each galaxy, and we show the profiles for each in Figure~\ref{fig:dm profile}. Increasing $v_{\rm c,max}$ while keeping $v_{\rm c}$ fixed at 500 pc serves to reduce dark matter density profile interior to 500 pc, broadening the potential well.

As the initial gas profile in each galaxy is smooth, we use initial supernova driving to prevent uniform collapse and a spurious starburst. We randomly place supernovae in the disk of the galaxy at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central HI surface density and the relation presented in \citep{Roychowdhury2009}. We stop the artificial driving 25~Myr after the first star particle forms.

%\begin{figure}
%\centering
%\includegraphics[width=0.8\linewidth]{dark_matter_mass_virial} \\
%\vspace{0.1cm}
%\includegraphics[width=0.8\linewidth]{circular_velocity_virial} \\
%\includegraphics[width=0.8\linewidth]{initial_surface_density}
%\caption{Dark matter cumulative mass (top) and circular velocity profiles (middle) for each of our galaxies, plotted as a fraction of the virial radius for each (see Table~\ref{table:IC} for details). The cumulative mass interior to 500 pc is held fixed in each galaxy, at $2.5\times 10^7$ M$_{\odot}$, with the variations in profile arising from changing the scale radius. The bottom panel gives the initial gas surface density profiles for each galaxy, which are essentially the same.}
%\ref{fig:dm profile}

\section{Results}

\section{Discussion}

\section{Conclusion}

\acknowledgments
Acknowledgments.

\facilities{Yeti, CCA cluster, Stampede, Pleiades} 
\software{Numpy, Enzo, yt, astropy}
